Marine species do not need visas: the transboundary nature of the world’s exploited marine species

### 2020-08-11 Scripts/Manuscript_Draft.Rmd
Fixed quality check comments
Fixed legends requested by journal

![**Figure 1.** Number of transboundary species and their contribution to global fisheries catches and revenue. A) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively. B) Contribution of transboundary species to regional revenue (left) and catch (right). Regions according to the United Nations sub-regions: E. = Eastern, N. = Northern, S. = Southern, W. = Western, Ltn. Ame. & the Car. = Latin America and the Caribbean. Points = regional  mean ± sd. Revenue in 2019 real USD.](../Figures/Fig1.png)

@@

![Figure 2. Weighted benefits of transboundary species by $km^{2}$ and UN sub-region. A) Revenue in thousand 2019 USD. B) Catch in tonnes. Points are sub-region averages $\pm$ s.d. by country](../Figures/Fig2.png)

@@

![Figure 3. Number of transboundary species by catch trend and EEZ. Category A, Growing trend; Category B, Constant trend; Category C, Shrinking trend.“No Category” reflect species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data.](../Figures/Fig3.png)

@@

![Figure 4. Number of EEZs shared by transboundary species. A) Number of EEZs by species organized by associated habitat according to FishBase. Showing only species that share > 20 EEZs. B) Average catch between 2005 and 2014 of top five fishing countries capturing the top five shared species of each ecosystem preference (shown in bold on a). Note that there could be > 5 species due to similar sharing values. ** The category "Other" consists of species that have no classification according to FishBase.**](../Figures/Fig4.png)

@@

All analyses were run using the statistical software *R version 3.5.2 (2018-12-20)* with the packages *data.table* [@Packagedatatable:2019uh], *janitor* [@PackagejanitorSim:2018ur], *wesanderson* [@Packagewesanderson:2018vn], *rfishbase* [@PackagerfishbaseR:2019th], *R.matlab* [@PackageRmatlabRe:2018un], *sf* [@PackagesfSimpleF:2018vp], *sp* [@PackagespClasses:2019tn], *tidiverse* [@PackagetidyverseE:2017vq], *tidytext* [@PackagetidytextTe:2019vk], and *zoo* [@PackagezooSInfr:2019tm]. All code is available at https://github.com/jepa/FishForVisa. We performed a series of one-way analysis of variance (one-way ANOVA) and Multivariate analysis of variance (MANOVA) to determine statistically significant differences between the means of different groups (e.g., geographical regions, species, catch trends) of transboundary species and their contribution to catch and fishing revenue [@Chambers:1992up; @Krzanowski:1990wm]. We used the standard *R* functions for the ANOVA and MANOVA after testing for assumptions. In cases where the ANOVA assumptions were not clearly met we ran the non-parametric version Kruskal-Wallis Rank Sum Test to confirm the results [@Hollander:2013wz].

>>>>

![**Figure 1.** Number of transboundary species and their contribution to global fisheries catches and revenue. A) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively. B) Contribution of transboundary species to regional revenue (left) and catch (right). Regions according to the United Nations sub-regions: E. = Eastern, N. = Northern, S. = Southern, W. = Western, Ltn. Ame. & the Car. = Latin America and the Caribbean. Points = regional  mean ± sd. Revenue in 2019 real USD. Figure created using R version 3.5.2. Land and EEZ shapefiles from Natural Earth (www.naturalearthdata.com) and Sea Around Us (www.seaaroundus.org), respectively.](../Figures/Fig1.png)

@@

![Figure 2. Weighted benefits of transboundary species by $km^{2}$ and UN sub-region. A) Revenue in thousand 2019 USD. B) Catch in tonnes. Points are sub-region averages $\pm$ s.d. by country. Figure created using R version 3.5.2.](../Figures/Fig2.png)

@@

![Figure 3. Number of transboundary species by catch trend and EEZ. Category A, Growing trend; Category B, Constant trend; Category C, Shrinking trend.“No Category” reflect species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data. Figure created using R version 3.5.2.](../Figures/Fig3.png)

@@

![Figure 4. Number of EEZs shared by transboundary species. A) Number of EEZs by species organized by associated habitat according to FishBase. Showing only species that share > 20 EEZs. B) Average catch between 2005 and 2014 of top five fishing countries capturing the top five shared species of each ecosystem preference (shown in bold on a). Note that there could be > 5 species due to similar sharing values. ** The category "Other" consists of species that have no classification according to FishBase. Figure created using R version 3.5.2.**](../Figures/Fig4.png)

@@

All analyses were run using the statistical software *R version 3.5.2 (2018-12-20)* with the packages *data.table* [@Packagedatatable:2019uh], *janitor* [@PackagejanitorSim:2018ur], *wesanderson* [@Packagewesanderson:2018vn], *rfishbase* [@PackagerfishbaseR:2019th], *R.matlab* [@PackageRmatlabRe:2018un], *sf* [@PackagesfSimpleF:2018vp], *sp* [@PackagespClasses:2019tn], *tidiverse* [@PackagetidyverseE:2017vq], *tidytext* [@PackagetidytextTe:2019vk], and *zoo* [@PackagezooSInfr:2019tm]. All code is available at https://github.com/jepa/FishForVisa. All maps were made with Natural Earth data available at https://www.naturalearthdata.com/. We performed a series of one-way analysis of variance (one-way ANOVA) and Multivariate analysis of variance (MANOVA) to determine statistically significant differences between the means of different groups (e.g., geographical regions, species, catch trends) of transboundary species and their contribution to catch and fishing revenue [@Chambers:1992up; @Krzanowski:1990wm]. We used the standard *R* functions for the ANOVA and MANOVA after testing for assumptions. In cases where the ANOVA assumptions were not clearly met we ran the non-parametric version Kruskal-Wallis Rank Sum Test to confirm the results [@Hollander:2013wz].
